Over Twenty Years of Virtual Machine Development and Debugging Through Simulation

### 2018-08-15 paper.tex
write library correctly damn it

When programming with Smalltalk, the programmers usually starts from a snapshot which contains the core libraries, the development environment and the application developed. Development of the application consists essentially in writing and editing code, which effectively installs, modifies and removes compiled methods and classes from the set of live objects. When the changes are done, the developer takes a new snapshot, which includes its changes. Deployment is performed using a snapshot containing the deployed application and the required core librairies (unused librairies and development tools may be removed from the deployed snapshot to decrease memory footprint and for security purposes).

>>>>

When programming with Smalltalk, the programmers usually starts from a snapshot which contains the core libraries, the development environment and the application developed. Development of the application consists essentially in writing and editing code, which effectively installs, modifies and removes compiled methods and classes from the set of live objects. When the changes are done, the developer takes a new snapshot, which includes its changes. Deployment is performed using a snapshot containing the deployed application and the required core libraries (unused libraries and development tools may be removed from the deployed snapshot to decrease memory footprint and for security purposes).
